Cost- and Deadline-Constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-04-24 paper/paper.tex
split evaluation section
new boxplots

\section{Evaluation}
\label{sec:performance}

@@

\subsection{Example of Results}

@@

\begin{figure*}[tb]
    \subfloat[Ratio of Actual Cost to Budget]{
        \includegraphics[width=0.45\textwidth]{run-finish-variations-test-0-output-cost-all}
        }
    \subfloat[Ratio of Actual Makespan to Deadline]{
        \includegraphics[width=0.45\textwidth]{run-finish-variations-test-0-output-makespan-all}
        }
    \caption[Boxplots for budget and deadline ratios when runtime estimates are inaccurate]{Boxplots for budget and deadline ratios when runtime estimate error varies from $\pm$0\% to $\pm$50\% for all three algorithms. A value of 1 indicates that the actual cost is equal to the budget, or the actual makespan is equal to the deadline, respectively. Values greater than 1 indicate that the budget/deadline has been exceeded.}
    \label{fig:variances}
\end{figure*}

@@

\begin{figure*}[tb]
    \subfloat[Ratio of Actual Cost to Budget]{
        \includegraphics[width=0.45\textwidth]{run-finish-delays-test-0-output-cost-montage-uniform_unsorted}
        }
    \subfloat[Ratio of Actual Makespan to Deadline]{
        \includegraphics[width=0.45\textwidth]{run-finish-delays-test-0-output-dagfinish-montage-uniform_unsorted}
        }
    \caption[Boxplots for budget and deadline ratios when provisioning delays occur]{Boxplots for budget and deadline ratios when provisioning delay varies from 0 seconds to 15 minutes for all three algorithms. A value of 1 indicates that the actual cost is equal to the budget, or the actual makespan is equal to the deadline, respectively. Values greater than 1 indicate that the budget/deadline has been exceeded.}
    \label{fig:delays}
\end{figure*}

@@

\begin{figure*}[tb]
    \subfloat[Ratio of Actual Cost to Budget]{
        \includegraphics[width=0.45\textwidth]{run-finish-failures-test-0-output-cost-all}
        }
    \subfloat[Ratio of Actual Makespan to Deadline]{
        \includegraphics[width=0.45\textwidth]{run-finish-failures-test-0-output-makespan-all}
        }
    \caption{Boxplots for budget and deadline ratios when failure rate varies
    from 0 seconds to 50 \% for all three algorithms. A value of 1
    indicates that the actual cost is equal to the budget, or the actual makespan is equal to the deadline, respectively. Values greater than 1 indicate that the budget/deadline has been exceeded.}
    \label{fig:failures}
\end{figure*}

>>>>

\section{Evaluation Metods}
\label{sec:performance}

@@

\section{Discussion of Results}
\subsection{Results Example}

@@

\begin{figure*}[tb]
    \subfloat[Ratio of Actual Cost to Budget]{
        \includegraphics[width=0.4\textwidth]{run-finish-variations-test-0-output-cost-all}
        }
    \subfloat[Ratio of Actual Makespan to Deadline]{
    \hspace{2cm}
        \includegraphics[width=0.4\textwidth]{run-finish-variations-test-0-output-makespan-all} }
    \caption[Boxplots for budget and deadline ratios when runtime estimates are inaccurate]{Boxplots for budget and deadline ratios when runtime estimate error varies from $\pm$0\% to $\pm$50\% for all three algorithms. A value of 1 indicates that the actual cost is equal to the budget, or the actual makespan is equal to the deadline, respectively. Values greater than 1 indicate that the budget/deadline has been exceeded.}
    \label{fig:variances}
\end{figure*}

@@

\begin{figure*}[tb]
    \subfloat[Ratio of Actual Cost to Budget]{
        \includegraphics[width=0.4\textwidth]{run-finish-delays-test-0-output-cost-montage-uniform_unsorted}
        }
    \subfloat[Ratio of Actual Makespan to Deadline]{
        \hspace{2cm}
        \includegraphics[width=0.4\textwidth]{run-finish-delays-test-0-output-dagfinish-montage-uniform_unsorted}
        }
    \caption[Boxplots for budget and deadline ratios when provisioning delays occur]{Boxplots for budget and deadline ratios when provisioning delay varies from 0 seconds to 15 minutes for all three algorithms. A value of 1 indicates that the actual cost is equal to the budget, or the actual makespan is equal to the deadline, respectively. Values greater than 1 indicate that the budget/deadline has been exceeded.}
    \label{fig:delays}
\end{figure*}

@@

\begin{figure*}[tb]
    \subfloat[Ratio of Actual Cost to Budget]{
        \includegraphics[width=0.4\textwidth]{run-finish-failures-test-0-output-cost-all}
        }
    \subfloat[Ratio of Actual Makespan to Deadline]{
        \hspace{2cm}
        \includegraphics[width=0.4\textwidth]{run-finish-failures-test-0-output-makespan-all}
        }
    \caption{Boxplots for budget and deadline ratios when failure rate varies
    from 0 seconds to 50 \% for all three algorithms. A value of 1
    indicates that the actual cost is equal to the budget, or the actual makespan is equal to the deadline, respectively. Values greater than 1 indicate that the budget/deadline has been exceeded.}
    \label{fig:failures}
\end{figure*}
